A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-07-10 paper/theor-experiment.tex
adding tba beam line

\begin{figure}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig1) at (0,0)
	{\includegraphics[width=0.9\textwidth]{Report/awa-drawing}};
	\node[fill=white, inner sep=2pt] (txt2) at (35,15) {Interferometer};
	\node[fill=white, inner sep=2pt, rotate=26] (txt2) at (18,19.5) {Slit};	
	\node[fill=white, inner sep=2pt, rotate=20] (txt2) at (13,27) {Window};
	\end{tikzpicture}
	\caption{High charge beam line layout at the AWA.}
	\label{awa-pic}
\end{figure}
%\vspace{-1em}
In addition to the physics challenges, we chose this model to demonstrate the ability of the framework to tackle large problems.
Six design variables and objectives were used, 
along with three constraints.
The objectives include transverse and longitudinal beam size, 
transverse momentum and longitudinal energy spread. 
The design variables include the two gun solenoids and 
the first four quadrupoles. The objectives are calculated at 
$s_1=19.4$~[m], at the entrance of the fifth quadrupole in Fig.~\ref{awa-pic}.  
This problem encompasses high dimensionality 
and nonlinear effects such as space charge. There is no existing information
that accurately predicts where the Pareto front will fall. This work is also meaningful in that
it will guide future operations at the AWA.
\nrnote{Maybe eqs 5.10-5.21 and code example should move after time step scan and hyper parameters}

\begin{align}
\text{min}  \quad & \text{rms}_{x}\left(s = s_1\right), \quad \text{rms}_{y}\left(s = s_1\right) \label{eq:awa:p1}\\
& \text{rms}_{px}\left(s = s_1\right), \quad \text{rms}_{py}\left(s = s_1\right), \label{eq:awa:p2}\\
& \text{rms}_{s}\left(s = s_1\right), \quad dE \label{eq:awa:p4} \\
\text{subject to} \quad & rms_x(s=s_0) < 0.1 \, [m]\label{eq:awa:c1}\\
\quad & rms_y(s=s_0) < 0.1\, [m]\label{eq:awa:c2}\\
\quad & |rms_y(s=s_0) - rms_x(s=s_0) | < 0.005 \, [m]\label{eq:awa:c3}\\
\quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
\quad & \text{Volt}_{\text{Linac}} = 24-25\left[\text{MV/m}\right] \\
\quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
\quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
\quad & \phi_{\text{linac}} =-20^\circ \label{eq:awa:lastdvar}
\end{align}

>>>>

\begin{figure}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig1) at (0,0)
	{\includegraphics[width=0.9\textwidth]{Report/awa-drawing}};
	\node[fill=white, inner sep=2pt] (txt2) at (10,-10) {$s_1$};
	\node[fill=white, inner sep=2pt, rotate=26] (txt2) at (18,19.5) {Slit};	
	\end{tikzpicture}
	\caption{High charge beam line layout at the AWA.}
	\label{awa-linac}
\end{figure}

\begin{figure}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig2) at (0,0)
	{\includegraphics[width=\textwidth]{Report/tba_dogleg}};
	\node[fill=white, inner sep=2pt] (txt2) at (2,35) {$s_1$};
	\node[fill=white, inner sep=2pt] (txt2) at (14,35) {$s_2$};
	\node[fill=white, inner sep=2pt] (txt2) at (35,31) {$s_3$};
	\node[fill=white, inner sep=2pt] (txt2) at (24,50) {Septum};
	\draw [blue, ->, line width=1] (30,50) -- (30, 42);	
	\node[fill=white, inner sep=2pt] (txt2) at (5,50) {Kicker};
	\draw [blue, ->, line width=1] (10,50) -- (18, 43);
	\end{tikzpicture}
	\caption{Continuation of the high charge beam line layout at the AWA. 
		This is the the two beam acceleration section.}
	\label{awa-tba}
\end{figure}

%\vspace{-1em}
In addition to the physics challenges, we chose this model to demonstrate the ability of the framework to tackle large problems.
Six design variables and objectives were used, 
along with three constraints.
The objectives include transverse and longitudinal beam size, 
transverse momentum and longitudinal energy spread. 
The design variables include the two gun solenoids and 
the first four quadrupoles. The objectives are calculated at 
$s_1=19.4$~[m], at the entrance of the fifth quadrupole in Fig.~\ref{awa-pic}.  
This problem encompasses high dimensionality 
and nonlinear effects such as space charge. There is no existing information
that accurately predicts where the Pareto front will fall. This work is also meaningful in that
it will guide future operations at the AWA.
\nrnote{Maybe eqs 5.10-5.21 and code example should move after time step scan and hyper parameters}

\begin{align}
\text{min}  \quad & \text{rms}_{x}\left(s = s_3\right), \quad \text{rms}_{y}\left(s = s_3\right) \label{eq:awa:p1}\\
& \text{rms}_{px}\left(s = s_3\right), \quad \text{rms}_{py}\left(s = s_3\right), \label{eq:awa:p2}\\
& \text{rms}_{s}\left(s = s_3\right), \quad dE \label{eq:awa:p4} \\
\text{subject to} \quad & rms_x(s=s_1) < 0.1 \, [m]\label{eq:awa:c1}\\
\quad & rms_y(s=s_1) < 0.1\, [m]\label{eq:awa:c2}\\
\quad & |rms_y(s=s_1) - rms_x(s=s_1) | < 0.005 \, [m]\label{eq:awa:c3}\\
\quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
\quad & \text{Volt}_{\text{Linac}} = 24-25\left[\text{MV/m}\right] \\
\quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
\quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
\quad & \phi_{\text{linac}} =-20^\circ \label{eq:awa:lastdvar}
\end{align}
